### 2016-12-01 paper/chapters/vae.tex
objective +-> function

\subsection{Objective}
The objective function of the VAE consists of the reconstruction error and the regularizer.
%$\mathcal{L}$ learns both the encoder as well as the decoder with their respective parameters $\phi$ and $\theta$.
% probabilistic encoder $q_\phi(z|x)$ (produces z values from which x could've been generated)
% probabilistic decoder $p_\theta(x|z)$
We will discuss both terms in detail below.

>>>>

\subsection{Objective Function}
The objective function of the VAE consists of the reconstruction error and the regularizer.
%$\mathcal{L}$ learns both the encoder as well as the decoder with their respective parameters $\phi$ and $\theta$.
% probabilistic encoder $q_\phi(z|x)$ (produces z values from which x could've been generated)
% probabilistic decoder $p_\theta(x|z)$
We will discuss both terms in detail below following the derivation of the lower variational bound $\mathcal{L}$ and the rewritten objective function.
